% 提案システムの目的
\deleted{We propose an edge computing system that estimates the activity levels of office workers using a light-detection-and-ranging (LiDAR) sensor network.}
\revised{This paper proposes a system that estimates the activity levels of office workers using a light-detection-and-ranging (LiDAR) sensor network.}
% 点群の特徴抽出
\deleted{The system captures point-cloud data of individuals at work obtained by LiDAR, converting it into numerical features for analysis.}
\revised{Point-cloud data of individuals at work are captured by LiDAR and converted into numerical features.}
% 機械学習による推論
Machine learning models are employed to estimate the activity levels from the features.
% 評価実験
\deleted{To evaluate the system, we conducted experiments in experimental office environments, collecting point-cloud data while participants watched educational videos.}
\revised{Evaluation experiments were conducted in office environments while participants watched educational videos.}
% 活動レベルの評価
Activity indicators were derived from tests and questionnaires, and binary labels were generated using clustering for model evaluation.
% モデルの評価
\deleted{We developed several models utilizing different data types and feature extraction techniques, assessing their performance against the binary labels.}
\revised{Several models utilizing different feature types were developed and assessed against the binary labels.}
\revised{Activity level is defined as the degree of concentration during PC-based deskwork.
Image-based and centroid-based features were extracted from point-cloud data.}
% 結果
\deleted{Our results demonstrated the effectiveness of the proposed system for estimating activity levels based on a range of three-dimensional features.}
\revised{The results demonstrate that three-dimensional features are effective for activity-level estimation.}
