%
\deleted{We conducted evaluation experiments in office environments, focusing on PC-based deskwork, to assess human activity levels using our proposed system.
%
In a typical office department, a group typically consists of around 10 to 15 members who share certain professional attributes (e.g., accounting or development experience).
%
Accordingly, we recruited participants to reflect these real-world compositions, ensuring they had similar backgrounds relevant to the task.
%
Our experimental scenario involved ``taking notes while viewing learning video content and taking a quiz afterward.''\footnote{Our experiment was approved by the Ethics Committee of Shibaura Institute of Technology.}
%
We measured the activity levels from subjective and objective perspectives.
%
The subjective evaluation was based on prior knowledge and comprehension of the content of the learning video, while the objective evaluation was based on quiz scores.
We conducted data-acquisition experiments to evaluate the features for assessing activity levels using multiple short learning videos.}
\revised{Evaluation experiments were conducted in office environments for PC-based deskwork.\footnote{The experiment was approved by the Ethics Committee of Shibaura Institute of Technology.}
Participants with similar professional backgrounds were recruited to reflect typical office group compositions of 10 to 15 members.
The scenario involved taking notes while viewing learning video content and taking a quiz afterward.
Activity levels were measured from subjective evaluation based on prior knowledge and comprehension, and objective evaluation based on quiz scores.
Data-acquisition experiments used multiple short learning videos.}
\revised{The learning-video scenario simulates sustained PC-based deskwork with note-taking and comprehension assessment.
Quiz scores provide objective indicators of content mastery.
Questionnaire responses provide subjective indicators of prior knowledge and comprehension.}
