%
\deleted{Each participant brought their own laptop and placed it on the desk and was asked to follow a series of steps, from viewing a learning video to answering a questionnaire.
%
The scenario and conditions of the experiment, under which participants viewed a video and took a quiz, were explained.
%
A learning video, a notepad, a quiz about the video content, and a questionnaire were provided to each participant.
%
A participant began viewing the learning video and taking notes upon receiving a signal to start.
The participant stopped viewing and taking notes when the video finished.
%
The participant then took the quiz and completed the questionnaire.
%
Google Forms was used for the quiz and questionnaire.
%
The participants were allowed to refer to their notes during the quiz.
%
After the quiz, they completed the questionnaire.
%
The steps were repeated for a set of learning videos.
The above steps were carried out by all participants.}
\revised{Each participant used a personal laptop and followed steps from viewing a learning video to answering a quiz and questionnaire via Google Forms.
Notes could be referred to during the quiz.
The steps were repeated for each learning video.}
\revised{Each participant received a learning video, notepad, quiz, and questionnaire.
Video viewing and note-taking started and stopped on an experimenter signal.
The quiz was completed before the questionnaire for each video.}

%
The participants in the experiment were 37 students from Shibaura Institute of Technology.
  %
  Their ages ranged from 19 to 24.
  % %
  % The experiment was conducted from December 14th to 20th, 2022.
%
Three learning videos about structured query language (SQL) were examined~\cite{SQL}.
%
The durations of the videos were 206, 167, 116.
%
\deleted{A quiz was created for each video, as shown in Table~\ref{quiz_train}.
  %
  The quizzes were administered to ascertain the content of each video.
  %
  The time for answering all the quizzes was limited to within 300 s.
  %
  A questionnaire was conducted for each video to survey comprehension of the video content.
  %
  The questionnaire asked participants to rate their understanding and prior knowledge of the learning videos on a scale from 1 to 5.}
\revised{A quiz was created for each video, as shown in Table~\ref{quiz_train}.
  The quiz time limit was 300 s.
  A questionnaire rated understanding and prior knowledge on a scale from 1 to 5.}
