\deleted{Table \ref{matrix_xg_train} shows the confusion matrices of five XGBoost models, four with a single feature and one with all features. 
% 
Table \ref{matrix_xg_train_a} shows the confusion matrix of the model with image-based 50th percentile values as input features. 
% 
The model showed a trend toward high FNR and lower FPR.
% 
Table \ref{matrix_xg_train_b} shows the confusion matrix of the model with image-based 90th percentile values as input features. 
% 
The model showed a trend toward high FNR and lower FPR.
%
Table \ref{matrix_xg_train_c} shows the confusion matrix of the model with centroid 50th percentile values as input features. 
% 
The model showed a trend toward moderate FNR and slightly lower FPR. 
%
Table \ref{matrix_xg_train_d} shows the confusion matrix of the model with centroid 90th percentile values as input features. 
% 
The model showed a trend toward moderate FNR and slightly lower FPR.
% 
Table \ref{matrix_xg_train_e} shows the confusion matrix of the model with all feature values as input. 
% 
The model showed a trend toward moderate FNR and slightly lower FPR.
% 

Table \ref{result_xg_train} shows the metrics of each XGBoost model. 
% 
A comparative evaluation of the five models was conducted.
%
The model with the lowest FNR was the one using centroid 90th percentile values.
%
The model with the lowest FPR was the one using image-based 50th percentile values.
%
The model with the highest accuracy was the one using all features. 

%
Table \ref{feature_importance_xg} shows the feature importance computed from the XGBoost model that uses all feature values as input (Table \ref{matrix_xg_train_e}).
%
The feature importance indicated the highest values for the centroid features Centroid-50th and Centroid-90th.
% 
The following inferences about activity levels were derived based on the model-accuracy comparisons and feature importance. 
%
It was found that centroid features were effective in reducing misclassifications among similar activity levels.
% 
It was also found that the model using all features achieved the highest accuracy among the five models. 
%
From these results, we confirmed that employing a diverse set of features derived from three-dimensional information is effective for estimating activity levels in short-video datasets when using an XGBoost-based model.}
\revised{Table~\ref{matrix_xg_train} shows confusion matrices of five XGBoost models: four with a single feature and one with all features.
Table~\ref{result_xg_train} shows the evaluation metrics.
The all-feature model achieved the highest accuracy.
The model with centroid 90th percentile values achieved the lowest FNR.
Table~\ref{feature_importance_xg} shows feature importance from the all-feature model (Table~\ref{matrix_xg_train_e}).
Centroid-50th and Centroid-90th showed the highest importance.
Centroid features reduced misclassifications among similar activity levels.
A diverse set of three-dimensional features is effective for activity-level estimation with XGBoost on short-video datasets.}
\revised{For the XGBoost model, the all-feature input outperformed every single-feature model in Table~\ref{result_xg_train}.
The contrast between RF and XGBoost indicates that complementary 3D features require an appropriate ensemble model to be fully exploited.}
