\deleted{Table \ref{matrix_rf_train} shows the confusion matrices of five RF models, four with a single feature and one with all features. 
% 
Table \ref{matrix_rf_train_a} shows the confusion matrix of the model with image-based 50th percentile values as input features. 
% 
The model showed a trend toward moderate FNR and slightly lower FPR.
% 
Table \ref{matrix_rf_train_b} shows the confusion matrix of the model with image-based 90th percentile values as input features. 
% 
The model showed a trend toward slightly higher FNR and lower FPR.
%
Table \ref{matrix_rf_train_c} shows the confusion matrix of the model with centroid 50th percentile values as input features. 
%
The model showed a trend toward moderate FNR and slightly lower FPR.
%
Table \ref{matrix_rf_train_d} shows the confusion matrix of the model with centroid 90th percentile values as input features. 
% 
The model showed a trend toward moderate FNR and slightly lower FPR.
% 
Table \ref{matrix_rf_train_e} shows the confusion matrix of the model with all feature values as input. 
% 
The model showed a trend toward slightly higher FNR and lower FPR.
% 

Table \ref{result_rf_train} shows the evaluation metrics of each RF model. 
% 
A comparative evaluation of the five models was conducted. 
%
The model with the lowest FNR was the one using centroid 90th percentile values.
%
The model with the lowest FPR was the one using image-based 50th percentile values.
%
The model with the highest accuracy was the one using image-based 50th percentile values. 

%
Table \ref{feature_importance_rf} shows the feature importance computed from the RF model that uses all feature values as input (Table \ref{matrix_rf_train_e}).
%  
The feature importance indicated the highest values for the centroid features Centroid-50th and Centroid-90th.
% 
The following inferences about activity levels were derived based on the model-accuracy comparisons and feature importance. 
%
It was found that centroid features were effective in reducing misclassifications among similar activity levels.
%
It was also found that image-based 50th percentile values achieved the highest accuracy among the five models.
% 
These results indicate that different 3D feature types provide complementary information for estimating activity levels in short-video datasets.
  %
  The highest accuracy was achieved with a single image-based feature rather than with all features combined.}
\revised{Table~\ref{matrix_rf_train} shows confusion matrices of five RF models: four with a single feature and one with all features.
Table~\ref{result_rf_train} shows the evaluation metrics.
The model with image-based 50th percentile values achieved the highest accuracy.
The model with centroid 90th percentile values achieved the lowest false negative rate (FNR).
Table~\ref{feature_importance_rf} shows feature importance from the all-feature model (Table~\ref{matrix_rf_train_e}).
Centroid-50th and Centroid-90th showed the highest importance.
Centroid features reduced misclassifications among similar activity levels.
Image-based 50th percentile values achieved the highest accuracy among the five models.
Different 3D feature types provide complementary information for short-video datasets.}
\revised{For the RF model, the all-feature input did not outperform the image-based 50th percentile single-feature model in Table~\ref{result_rf_train}.
Image-based 50th percentile values showed moderate false negative rate (FNR) and slightly lower false positive rate (FPR) in Table~\ref{matrix_rf_train_a}.
Centroid 90th percentile values achieved the lowest FNR among the single-feature models.}
