\deleted{The LiDAR-sensor network technology, with its high-precision distance measurement capabilities, has been widely applied across various fields.
It has been particularly used in areas such as environmental monitoring, autonomous driving, and smart city infrastructure, opening up new possibilities in each domain \cite{9090850,Sun_2021_CVPR,8846588,8737958}.
Our study differs by applying LiDAR-sensor-network technology to office environments, focusing on estimating the activity levels of office workers.

Yan et al.\ presented a LiDAR-based multi-task road perception network (LMRoadNet) designed for autonomous vehicles \cite{9090850}.
The network incorporates a lightweight and efficient multi-task learning model that simultaneously executes occlusion-free road segmentation, road-height estimation, and road-topology recognition.
The model demonstrated high precision in real-time performance, surpassing conventional multi-task architectures and achieving results comparable to state-of-the-art methods.
LMRoadNet was shown to be an effective tool for practical autonomous-driving applications, offering a wide field of view while minimizing computational costs.

Sun et al.\ presented the Range Sparse Net (RSN) for efficient and accurate 3D object detection based on LiDAR \cite{Sun_2021_CVPR}.
The method uses a simple and efficient approach that predicts foreground points from range images and applies sparse convolutions on the selected points to detect objects.
RSN demonstrated superior accuracy and efficiency on the Waymo Open Dataset, achieving the best results in LiDAR-based pedestrian and vehicle detection.
RSN has proven to be an effective method for autonomous driving systems, providing higher detection performance and faster execution speeds necessary for extensive detection ranges.

Yu et al.\ presented a hybrid capsule network for land-cover classification using multispectral LiDAR data \cite{8846588}.
They converted the multispectral LiDAR data into feature images to use both geometrical and spectral properties.
A hybrid capsule network was then developed to extract both local and global entity-oriented features for accurate land-cover classification.
Quantitative evaluations on two datasets showed that the method achieved an overall accuracy of over 97.89\%.
It demonstrated superior accuracy and robustness compared with five other methods.
The hybrid capsule network proved effective, outperforming traditional approaches in land-cover classification using multispectral LiDAR data.

Lv et al.\ presented ``LiDAR-Enhanced Connected Infrastructure'' for providing high-resolution traffic information for smart cities \cite{8737958}.
The system detects the high-resolution real-time status of surrounding traffic participants using roadside LiDAR sensors and broadcasts this information to connected vehicles via dedicated short-range communications.
Initial tests at an intersection in Reno, Nevada, demonstrated the system's ability to accurately collect and distribute information about unconnected vehicles and pedestrians in real-time.
The system is expected to improve traffic safety, mobility, and fuel efficiency.
The study showed that the LiDAR-Enhanced Connected Infrastructure is a promising solution for integrating and providing real-time traffic information in smart cities, including data from unconnected road users.}
\revised{LiDAR-sensor networks have been applied to autonomous driving, land-cover classification, and smart-city traffic monitoring \cite{9090850,Sun_2021_CVPR,8846588,8737958}.
The present study applies LiDAR-sensor-network technology to office environments for activity-level estimation.
Yan et al.\ presented LMRoadNet for autonomous-driving road perception \cite{9090850}.
Sun et al.\ presented RSN for LiDAR-based 3D object detection \cite{Sun_2021_CVPR}.
Yu et al.\ presented a hybrid capsule network for land-cover classification \cite{8846588}.
Lv et al.\ presented LiDAR-enhanced connected infrastructure for smart-city traffic \cite{8737958}.}
\revised{Prior LiDAR applications target outdoor or infrastructure-scale sensing.
Office deskwork requires non-contact estimation of subtle upper-body movements at desk scale.}
