Physical activity in office environments is considered a critical factor in maintaining employee health and productivity \cite{PAPAGIANNIDIS2020102027}.
\deleted{Various studies have explored methods for monitoring and estimating the activity levels of people working in office environments.
Existing studies have attempted to assess such activity levels through surveys and external factors.
Our study differs by proposing the estimation of activity levels that incorporate 3D features.

Rongen et al.\ presented a systematic review and meta-analysis to evaluate the effectiveness of workplace health promotion programs (WHPPs) \cite{RONGEN2013406}.
The study focused on WHPPs targeting smoking cessation, physical activity, healthy nutrition, and obesity, and their impact on self-perceived health, sickness absence, work productivity, and work ability, based on randomized controlled trials (RCTs).
The study revealed that WHPPs generally had small overall effects, with greater effectiveness observed in younger populations, interventions involving weekly contact, and when no health promotion was offered to the control group.
The study concluded that the effectiveness of WHPPs is heavily dependent on the content of the interventions and the characteristics of the participants, emphasizing the need for high-quality RCTs to evaluate such programs.

Al Horr et al.\ presented a study reviewing literature to understand the relationship between indoor environmental quality (IEQ) and occupant productivity in office environments \cite{ALHORR2016369}.
The study reviewed over 300 papers from 67 journals, conference articles, and books, analyzing the effect of eight key IEQ factors on productivity and their physical parameters.
The study confirmed the significant effect of these factors on occupant productivity, highlighting the importance of interactions between them.
The study serves as a comprehensive resource for understanding the relationship between IEQ and productivity and provides valuable insights for future research in office environments.

Dishman et al.\ presented a meta-analysis to assess the effectiveness of workplace physical-activity interventions \cite{DISHMAN1998344}.
The study reviewed 26 interventions aimed at increasing physical activity or fitness levels at worksites, quantitatively evaluating their effects through meta-analysis.
The results indicated that most workplace interventions did not produce statistically significant increases in physical activity or fitness.
The analysis revealed that many of the studies were of low scientific quality, which could lead to an overestimation of the effects.
The study concluded that while workplace interventions are commonly implemented, there is a lack of high-quality evidence to support their effectiveness, underscoring the need for more rigorous research.

Nooijen et al.\ presented a study to investigate the barriers and facilitators for reducing sedentary behavior among office workers \cite{de2005effect}.
The study surveyed office workers from two Swedish companies to identify common barriers and facilitators and objectively measured sitting time using inclinometers.
The most frequently reported barrier was the habitual nature of sitting, while standing or walking meetings were identified as effective facilitators for reducing sedentary behavior.
The study also found differences in barriers and facilitators based on factors such as age, gender, and education levels.
The study concluded that individualized support and cultural or social changes in the workplace are essential for effectively reducing sedentary behavior among office workers.}
\revised{Existing studies assessed office activity levels through surveys and external factors \cite{RONGEN2013406,ALHORR2016369,DISHMAN1998344,de2005effect}.
The present study estimates activity levels from 3D features extracted from point-cloud data.}
\revised{Rongen et al.\ reported small overall effects of workplace health promotion programs and emphasized the need for high-quality randomized controlled trials \cite{RONGEN2013406}.Al Horr et al.\ confirmed that indoor environmental quality factors significantly affect occupant productivity \cite{ALHORR2016369}.
Dishman et al.\ found limited statistically significant effects from workplace physical-activity interventions and noted low scientific quality in many studies \cite{DISHMAN1998344}.
Nooijen et al.\ identified habitual sitting as a major barrier to reducing sedentary behavior \cite{de2005effect}.
Survey-based and environmental-factor approaches do not capture individual deskwork movements during task execution.}
