\begin{deletedblock}
Each participant brought their own laptop and placed it on the desk and was asked to follow a series of steps, from viewing a learning video to answering a questionnaire.
We explained the scenario and conditions of our experiment under which they would be viewing a video and taking a quiz.
We gave a learning video, a notepad, a quiz about the video content, and a questionnaire to each participant.
A participant began viewing the learning content and taking notes upon receiving a signal to start and stopped viewing and taking notes when the video finished.
The participant then took the quiz and completed the questionnaire.
We used Google Forms for the quiz and the questionnaire.
The participants were allowed to refer to their notes during the quiz.
After the quiz, the participants completed the questionnaire.
We used a single video; steps are not repeated.
The above steps were carried out by all participants.
The participants in the experiment were students from Shibaura Institute of Technology.
Their ages ranged from 19 to 24.
The experiment was conducted twice, from October 6th to 11th, 2022, and from November 11th to 18th, 2024.
We examined a single learning video on SQL~\cite{SQL}.
The duration of the video was 1398 s.
We created a quiz consisting of ten items on SQL query operations and table management.
The time limit for answering the quiz was 600~s.
We also administered a questionnaire consisting of two items on understanding and prior knowledge of the video content.
The questionnaire asked participants to rate their understanding and prior knowledge of the learning video on a scale from 1 to 5.
\end{deletedblock}
